### 2021-07-03 docs/manuscript/manuscript.tex
Fix deg range description

% For figure citations, please use "Fig" instead of "Figure".
In order to study three-node GRNs we represented them by three sets of real
numbers, the first set was composed of the interaction values
between genes in the network; the second of the diffusion rates (D) of each of
the three gene products; and the third of the degradation rates ($\delta$) of
these same gene products, with $D \in [0, 0.1]$ and $\delta \in [0, 0.05]$.\\

>>>>

% For figure citations, please use "Fig" instead of "Figure".
In order to study three-node GRNs we represented them by three sets of real
numbers, the first set was composed of the interaction values
between genes in the network; the second of the diffusion rates (D) of each of
the three gene products; and the third of the degradation rates ($\delta$) of
these same gene products, with $D \in [0, 0.1]$ and $\delta = \log_{2}phl$, where
$phl \in [5, 50]$ is the gene product half-life.\\
